babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-05-02 article.tex
Do not undersell

Currently, \verb;babette; does not replace all functionality in BEAUti,
as it does not provide 3 out of 7 tree priors, nor does it support RNA
alignments or use of morphological data. The many plug-ins of BEAUti
are not yet supported by \verb;babette;. \verb;babette; does not support
all command-line arguments of BEAST2, does not provide
the more specialized Tracer analysis options, nor is it as feature-rich
in plotting options as DensiTree. Up until now, the \verb;babette; features 
implemented are those requested by users. Further extension of \verb;babette; 
will be based on future user requests.

>>>>

Currently, \verb;babette; does not replace all functionality 
in BEAUti, BEAST2 and their many plug-ins.
This is reasonable, as these themselves also change in time.
\verb;babette; provides the majority of default tree priors and works only on DNA data. 
\verb;babette; supports the most important command-line arguments of BEAST2, provides
the core Tracer analysis options, and has the most basic subset of 
plotting options of DensiTree. Up until now, the \verb;babette; features 
implemented are those requested by users. Further extension of \verb;babette; 
will be based on future user requests.
